---
title: "Quarto Assignment - Exploring the mtcars Dataset"
author: Anusha Sarla (24219473)
format: pdf
execute:
  echo: false 
  warning: false
  message: false
---

# *Introduction*

The mtcars dataset, built into base R, contains performance and design metrics for **32 cars** from the 1970s, covering **11 variables** including miles per gallon (*mpg*), number of cylinders (*cyl*), horsepower (*hp*), and weight (*wt*).

In this document, we are exploring the relationship between a car's **weight** and its **fuel efficiency** (*miles per gallon*).

------------------------------------------------------------------------

# *Descriptive Statistics*

```{r}
summary(mtcars[, c("mpg", "wt")])
```

We focus on two important variables:

-   mpg: Miles per gallon (fuel efficiency)

-   wt: Weight of the car (in 1000 lbs)

# *Visualizing MPG vs Weight*

```{r}
# Created a scatter plot with the regression line
plot(mtcars$wt, mtcars$mpg,
     main = "Fuel Efficiency vs. Weight",
     xlab = "Weight (1000 lbs)",
     ylab = "Miles per Gallon (MPG)",
     pch = 19, col = "steelblue")

# Added the regression line
abline(lm(mpg ~ wt, data = mtcars), col = "red", lwd = 2)
```

*The scatter plot above shows that heavier cars tend to have lower fuel efficiency.* The **red line** is a simple linear regression fit, indicating a negative correlation.

# *Conclusion*

From the visualization and summary statistics, we conclude:

-   Heavier cars generally consume more fuel.

-   This negative correlation is clearly visible in the plot.

-   The mtcars dataset provides a good example of basic statistical exploration using R.
